%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer II - Azure Service Fabric} % Job title
    {Microsoft Corporation} % Organization
    {Redmond, Washington} % Location
    {Jan. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Focused on the Transactional Replicator used in Service Fabric Reliable Collections}
        \item {Aided in rebuilding the transactional replicator in C++ for native linux compatibility. Primarily working on interaction between transactional replicator and physical log component - including batched writes, truncation, and false progress detection.}
        \item {Built and maintained applications and performance infrastructure to benchmark replicator performance. Including end-to-end automated testing, unit and integration testing (primarily BOOST with C++)}
        \item {Created and maintained election simulation service fabric application designed to stress-test long-running clusters during up/downgrade. Composed of 5 microservices to drive simulation, with configuration options enabling Azure Storage backup and Azure Table Storage logging}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder, Lead Developer} % Organization
    {Coversplash/Photorankr} % Job title
    {Seoul, S.Korea} % Location
    {June. 2013 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined the Photorankr team as part of Princeton eLab’s 2013 incubator class scaling the network from 1,000 to over 9,000 users}
        \item {Key technical role as fullstack engineer, designing and deploying features of the site such as image lightbox, album creation, upload process and others.}
      \end{cvitems}
    }

\end{cventries}
